When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-03-28 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
changed panel mentions to a and b

The median NFC was `r mediannfc`, with $n=`r nrow(h3b_data[h3b_data$nfcmedian == "low",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ subjects below and $n=`r nrow(h3b_data[h3b_data$nfcmedian == "high",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ above the median.
We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`), so evidence was not in favour of H3a.
Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (left panel of Figure\ \@ref(fig:h3ac-plot)).
This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.

@@

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (right panel of Figure\ \@ref(fig:h3ac-plot)).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.

@@

The declining logistic $n$-back levels and $d'$ remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis, with betas that varied by less than 0.01.
In contrast to this stood the variability of the median RT betas, which ranged from about `r round(max(sca_results$beta_r), digits = 2)` to `r round(min(sca_results$beta_r), digits = 2)`, and reached significance in only one pipeline.
This pipeline was among the three pipelines with the highest $BF_{10}$, and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data beyond 2 $MAD$ from the median.
Interestingly, the curve of median RT betas in the upper panel of Figure\ \@ref(fig:sca-plot) mirrored the rectangular pipeline indicators in the transformation rows of the lower panel, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
As Fernandez et al.[-@Fernandez2020] found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond $\alpha=.05$, and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
Our data seems to corroborate this finding for $n$-back tasks as well.
Surprisingly, the $d'$ betas appear almost unaffected by the preprocessing pipeline, even though $d'$ was computed after the outlier exclusion.
This indicates that researchers who are interested in the correctness rather than the speed of responses can choose a simple preprocessing pipeline without risking false positives through elaborate transformations.

>>>>

The median NFC was `r mediannfc`, with $n=`r nrow(h3b_data[h3b_data$nfcmedian == "low",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ subjects below and $n=`r nrow(h3b_data[h3b_data$nfcmedian == "high",])/(nrow(h3b_data)/length(unique(h3b_data$subject)))`$ above the median.
We used an rmANOVA to investigate whether the difference between the SVs of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of the $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nlevels`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nlevels`), but neither a main effect of the NFC group (`r apa_print(hypothesis3a_model)$full_result$nfcmedian`, `r apa_print(hypothesis3a_BF_nlevel)$statistic$nfcmedian`) nor an interaction of NFC group and $n$-back level (`r apa_print(hypothesis3a_model)$full_result$nfcmedian_nlevels`), so evidence was not in favour of H3a.
Post-hoc tests showed that the difference between the SVs of 2- and 3-back is slightly more negative than the difference between 1- and 2-back (`r apa_print(pairs(hypothesis3a_emm_nlevel))$statistic`), but there were large inter-individual differences, especially for 2- and 3-back (Figure\ \@ref(fig:h3ac-plot)a).
This means that across the whole sample, there was a steeper decline in SVs from 2- to 3-back than from 1- to 2-back, but some participants showed a completely opposite pattern.

@@

With another rmANOVA we investigated whether the difference between the aversiveness scores of 1- and 2-back, and 2- and 3-back, respectively, depended on whether a participant's NFC score was above or below the median.
There was a main effect of NFC group (`r apa_print(hypothesis3c_model)$full_result$nfcmedian`, `r apa_print(hypothesis3c_BF_levels)$statistic$nfc`) and a main effect of the $n$-back level (`r apa_print(hypothesis3c_model)$full_result$nlevels`, `r apa_print(hypothesis3c_BF_levels)$statistic$levels`), but no interaction (`r apa_print(hypothesis3c_model)$full_result$nfcmedian_nlevels`).
In favour of H3c, post-hoc tests revealed that participants with NFC scores below the median reported higher aversiveness than participants with NFC scores above the median (`r apa_print(pairs(hypothesis3c_emm_nfc))$statistic`) (Figure\ \@ref(fig:h3ac-plot)b).
Regardless of NFC, the difference of the aversiveness scores of 2- and 3-back was smaller and more negative than that of 1- and 2-back (`r apa_print(pairs(hypothesis3c_emm_levels))$statistic`), but again, there were large inter-individual differences.
The full results of these analyses of NFC group differences can be found in Table S.11 to S.15 in the Supplementary Material.

@@

The declining logistic $n$-back levels and $d'$ remained significant predictors of SVs throughout all 63 preprocessing pipelines in the specification curve analysis, with betas that varied by less than 0.01.
In contrast to this stood the variability of the median RT betas, which ranged from about `r round(max(sca_results$beta_r), digits = 2)` to `r round(min(sca_results$beta_r), digits = 2)`, and reached significance in only one pipeline.
This pipeline was among the three pipelines with the highest $BF_{10}$, and applied inverse transformation to the RT data, across subjects but within conditions, and excluded data beyond 2 $MAD$ from the median.
Interestingly, the curve of median RT betas in Figure\ \@ref(fig:sca-plot)a mirrored the rectangular pipeline indicators in the transformation rows of Figure\ \@ref(fig:sca-plot)b, so the transformation choice influenced the median RT much more than the dimension or the exclusion choice did.
As Fernandez et al.[-@Fernandez2020] found, applying more than one preprocessing step to the reaction time data of a Stroop task increased the risk of false positives beyond $\alpha=.05$, and transformation choices inflated this risk more than outlier exclusion or aggregation choices did.
Our data seems to corroborate this finding for $n$-back tasks as well.
Surprisingly, the $d'$ betas appear almost unaffected by the preprocessing pipeline, even though $d'$ was computed after the outlier exclusion.
This indicates that researchers who are interested in the correctness rather than the speed of responses can choose a simple preprocessing pipeline without risking false positives through elaborate transformations.
